PyPy – status and next goals

### 2008-04-09 talk/rupy2008/talk.tex
Typos.  Minor clarification.

\begin{frame}
  \frametitle{.NET Integration}
  \begin{itemize}
  \item giving PyPy.NET similar capabilities as CPython
  \item accessing .NET libraries seamlessly from PyPy
  \item ... demo
  \end{itemize}
\end

@@

\begin{frame}
  \frametitle{Currently Working on: Just-in-Time Compiler}
  Problems:
  \begin{itemize}
  \item writing good JITs for dynamic languages is hard work
  \item keeping up with new language features is hard
  \item compilers are a bad encoding for languag semantics
  \pause
  \begin{block}{
    Existing hand-written JITs}
    \begin{itemize}
    \item Psyco (mostly unmaintained)
    \item LuaJit (slightly simpler language, genius at work)
    \item Tamarin (company support, who knows how good it is)
    \end{itemize}
  \end{block}
  \end{itemize}
  \pause
\end{frame}

\begin{frame}
  \frametitle{If you cannot write them, grow your own}
  \begin{itemize}
  \item If you cannot write a JIT, don't do that then
  \pause
  \item Idea: Automatically Generate the JIT from the interpreter
  \pause
  \end{itemize}
  \begin{block}{
    Partial Evaluation}
    \begin{itemize}
    \item old idea from CS research
    \item transforms an interpreter into a static compiler
    \item never worked well for real-life examples
    \item key insight: generating a JIT is \emph{easier}
    \end{itemize}
  \end{block}

@@

\begin{frame}
  \frametitle{JIT Generation: Current Status}
  \begin{itemize}
  \item we had a working prototype at the end of the EU project
  \item speeds up simple arithmetic functions \emph{a lot}
  \item had limitations that were hard to fix with
  \pause
  \item refactoring happened in the last two months to improve the situation
  \item still in progress, but already allows experimentation
  \item we used the new flexibility to try new, advanced things
  \item goes into the direction of a tracing JIT
  \item right now we are starting to hit the hard bits
  \item we hope to get really good results for more general code in a few months
  \item ... demo
  \end{itemize}
\end{frame}

>>>>

\begin{frame}
  \frametitle{.NET Integration}
  \begin{itemize}
  \item giving PyPy.NET similar capabilities as CPython
  \item accessing .NET libraries seamlessly from PyPy
  \item ... demo
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Currently Working on: Just-in-Time Compiler}
  Problems:
  \begin{itemize}
  \item writing good JITs for dynamic languages is hard work
  \item keeping up with new language features is hard
  \item compilers are a bad encoding for language semantics
  \pause
  \begin{block}{
    Existing hand-written JITs}
    \begin{itemize}
    \item Psyco (mostly unmaintained)
    \item LuaJit (slightly simpler language, genius at work)
    \item Tamarin (company support, who knows how good it is)
    \end{itemize}
  \end{block}
  \end{itemize}
  \pause
\end{frame}

\begin{frame}
  \frametitle{If you cannot write them, grow your own}
  \begin{itemize}
  \item If you cannot write a JIT, don't do that then
  \pause
  \item Idea: Automatically Generate the JIT from the interpreter
  \pause
  \end{itemize}
  \begin{block}{
    Partial Evaluation}
    \begin{itemize}
    \item old idea from CS research
    \item transforms an interpreter into a static compiler
    \item never worked well for real-life examples
    \item key insight: generating a JIT is \emph{easier} than a static compiler
    \end{itemize}
  \end{block}

@@

\begin{frame}
  \frametitle{JIT Generation: Current Status}
  \begin{itemize}
  \item we had a working prototype at the end of the EU project
  \item speeds up simple arithmetic functions \emph{a lot}
  \item had limitations that were hard to fix
  \pause
  \item refactoring happened in the last two months to improve the situation
  \item still in progress, but already allows experimentation
  \item we used the new flexibility to try new, advanced things
  \item goes into the direction of a tracing JIT
  \item right now we are starting to hit the hard bits
  \item we hope to get really good results for more general code in a few months
  \item ... demo
  \end{itemize}
\end{frame}
